---
title: "p8105_hw6_zz3039"
output: github_document
date: "2022-11-30"
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
```

## Problem 2

```{r}
homi_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = paste(city, state, sep=", "),
    status = case_when(
      disposition %in% c("Closed by arrest", "Closed without arrest") ~ "solved",
      TRUE ~ "unsolved"),
    status = as.factor(status),
    victim_age = as.numeric(victim_age)) %>% 
  filter(city_state != "Dallas, TX",
         city_state != "Kansas City, MO",
         city_state != "Phoenix, AZ",
         city_state != "Tulsa, AL",
         victim_race == "White"|victim_race == "Black") %>% 
  select(city_state, everything(), - city, - state)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
bal_data = 
  homi_data %>% 
  filter(city_state == "Baltimore, MD")

  
```

