---
title: "p8105_hw6_zz3039"
output: github_document
date: "2022-11-30"
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)

set.seed(1)
```

## Problem 2

```{r}
homi_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = paste(city, state, sep=", "),
    status = case_when(
      disposition %in% c("Closed by arrest", "Closed without arrest") ~ "solved",
      TRUE ~ "unsolved"),
    status = as.factor(status),
    victim_age = as.numeric(victim_age),
    victim_sex = fct_relevel(victim_sex, "Female")) %>% 
  filter(city_state != "Dallas, TX",
         city_state != "Kansas City, MO",
         city_state != "Phoenix, AZ",
         city_state != "Tulsa, AL",
         victim_race == "White"|victim_race == "Black") %>% 
  select(city_state, everything(), - city, - state) %>% 
  drop_na()
```

obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
bal_data = 
  homi_data %>% 
  filter(city_state == "Baltimore, MD")

fit_bal = 
  glm(status ~ victim_age + victim_sex + victim_race, data = bal_data, family = binomial) 

fit_bal %>% 
  broom::glance()

fit_bal %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  mutate(term = str_replace(term, "^victim_", "Victim "),
         term = str_replace(term, "sex", "sex: "),
         term = str_replace(term, "race", "race: " )) %>% 
  knitr::kable(digits = 3)

bal_data %>% 
  modelr::add_predictions(fit_bal) %>% 
  mutate(fitted_prob = boot::inv.logit(pred))
```


## Problem 3

```{r chunk_data import}
bw_data = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names()

skimr::skim(bw_data)

bw_data = 
  bw_data %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))

skimr::skim(bw_data)
```

### Model fitting

As there have long held the belief in China that women should eat more during pregnancy, I decided to build a regression model to explore the influence of mothers' weight gain, mothers' weight before pregant and bmi before pregant on the children's birth weight. 

```{r chunk_propose a model_1}
bw_data = 
  bw_data %>% 
  mutate(
    mrace = recode_factor(mrace, "1" = "White","2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other")) 

bw_lm = lm(bwt ~ wtgain + ppwt + ppbmi, data = bw_data)
summary(bw_lm)

bw_lm %>% 
  plot(which = 2)

bw_data %>% 
  modelr::add_residuals(bw_lm) %>% 
  modelr::add_predictions(bw_lm) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_violin() +
  labs(
    title = "Residual vs Prediction in Linear Model",
    x = "Prediction Value",
    y = "Model Residual"
  )
```

The result showed that all three factors were significant in determining children's birth weigth. The Q-Q plot and violin plot showed that the residuals of the model roughly followed normal distribution.

### Model modifying

After confirming that all three factors' significance, I decided to explore if the three factors affect children's birth weight differently within different races of mothers. 

```{r chunk_propose a model_2}
bw_lm_nested = lm(bwt ~ wtgain*mrace + ppwt*mrace + ppbmi*mrace, data = bw_data)
summary(bw_lm_nested)

bw_lm_nested %>% 
  plot(which = 2)

bw_data %>% 
  modelr::add_residuals(bw_lm_nested) %>% 
  modelr::add_predictions(bw_lm_nested) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_violin() + facet_grid(~mrace) +
  labs(
    title = "Residual vs Prediction in Nested Model",
    x = "Prediction Value",
    y = "Model Residual"
  )
```

The result showed that the three factors have different influences on birth weight of children with different races of mothers. They were all most influential on children with Black mothers, no significant influence were showed on children with Asian mothers.

